Ferramenta para geração em tempo real de mundos virtuais pseudo-infinitos para jogos 3D

### 2009-02-20 master-thesis/dissertacao.tex
- Wrong .bib, but later I take care of it...
- Some images to add a little bit of salt to the text;

%==============================================================================
% Identificação do trabalho
%==============================================================================
\title{Ferramenta para geração de mundos virtuais pseudo-infinitos para jogos 3D MMO}

@@

%%=============================================================================
%% Abstract
%%=============================================================================
% resumo na outra língua
% como parametros devem ser passados o titulo, o nome do curso
% e as palavras-chave na outra língua, separadas por vírgulas
\begin{englishabstract}
{VXDL: A Language for Interconnection and Resources Specification in Virtual Grids}
{Programa de Pós-Graduação em Informática}
{virtualization, virtual grids, virtual clusters, resources description language}
Grid computing has been defined as an infrastructure integrator of distributed resources. Although it is already used on a large scale in many areas, this type of computational infrastructure is still an area of active research, with many open questions. Today, new research works investigate the application of resources virtualization techniques to perform the composition of virtual grids. These grids can be defined as a high level abstraction of resources (computing and network), through which users have a view of a wide range of interconnected computers, that can be selected and virtually organized. In a virtual grid, as well in a real grid, users and middleware must have tools that allow the composition and management of the infrastructure. Among these tools, there are languages for resource description that allow the specification of components that will be used in the infrastructure. In a virtualized environment, the resources descriptions languages should offer attributes that interact with some peculiarities, such as the possibility of allocate multiple virtual resources (computing and network) on the same physical resource. In this context, this work presents VXDL, a language developed for the interconnections and resources description in virtual grids. The innovations proposed in VXDL allow the description, classification and parameter specification of all desirable components, including network topology and virtual routers. VXDL also allow the specification of a execution timeline, which can assist grid middleware in the tasks of resources sharing and scheduling. To evaluate the proposed language, this work presentes I) a comparative study between VXDL and other resources description languages and II) an analysis of results obtained with the benchmarks execution in virtual infrastructures composed using different VXDL descriptions.
\end{englishabstract}

@@

%%=============================================================================
%% Lista de tabelas
%%=============================================================================
\listoftables

>>>>

%==============================================================================
% Identificação do trabalho
%==============================================================================
\title{Ferramenta para geração em tempo real de mundos virtuais pseudo-infinitos para jogos 3D}

@@

%%=============================================================================
%% Abstract
%%=============================================================================
% resumo na outra língua
% como parametros devem ser passados o titulo, o nome do curso
% e as palavras-chave na outra língua, separadas por vírgulas
\begin{englishabstract}
{English title here}
{Programa de Pós-Graduação em Informática}
{key word, word, key, english stuff}
Here we are supposed to write a english version of our portuguese description.
\end{englishabstract}

@@

%%=============================================================================
%% Lista de tabelas
%%=============================================================================
%\listoftables
